
\begin{thebibliography}{9}

\bibitem{intellijdoc} The jetbrains intelliji platform documentation, 
	\url{http://www.jetbrains.org/intellij/sdk/docs/basics/architectural_overview/file_view_providers.html}, June 2017.

\bibitem{ohmdoc} Ohm, a parser generator consisting of a library and a domain-specific language.
	\url{https://github.com/harc/ohm}, 2017.	

\bibitem{moldable} The Moldable Debugger: A Framework for Developing Domain-Specific Debuggers
	\url{https://link.springer.com/chapter/10.1007/978-3-319-11245-9_6}.

\bibitem{graphpars}A graph grammar approach to graphical parsing
	\url{http://ieeexplore.ieee.org/document/520809/}.

\bibitem{autumn1} 
Laurent Nicolas and Mens Kim.
Parsing Expression Grammars Made Practical.
SLE, 2015.

\bibitem{autumn2} 
Laurent Nicolas and Mens Kim.
Taming Context-Sensitive Languages with Principled Stateful Parsing.
SLE, 2016.	

\bibitem{} 
David R. Hanson and Jeffrey L. Korn. :
A Simple and Extensible Graphical Debugger.
Proceedings of the USENIX Annual Technical Conference, January 6-10, 1997. 173–184
% \url{https://www.usenix.org/legacy/publications/library/proceedings/ana97/full_papers/hanson/hanson.html}

\bibitem{}
petit parser
28. Renggli, L., Ducasse, S., Gˆırba, T., Nierstrasz, O.: Practical dynamic grammars
for dynamic languages. In: Proc. DYLA. (2010)

\bibitem{} TornadoFX
	\url{https://edvin.gitbooks.io/tornadofx-guide/content/4.%20Basic%20Controls.html}

\bibitem{} psi cookbook
	\url{http://www.jetbrains.org/intellij/sdk/docs/basics/psi_cookbook.html}

\bibitem{oracle_javafx} Oracle, javaFX
	\url{http://docs.oracle.com/javase/8/javase-clienttechnologies.htm}

\bibitem{tornadofx} TornadoFX guide
	\url{https://edvin.gitbooks.io/tornadofx-guide/content/1.%20Why%20TornadoFX.html}

\bibitem{antlr} Terence J. Parr. The Definitive ANTLR Reference: Building Domain-Specific Languages. 
	The Pragmatic Programmers, 2007. ISBN 0-9787392-5-6.

\bibitem{} \texttt{Terence Parr, Jean Bovet.} ANTLRWorks: An ANTLR Grammar Development Environment, UNPUBLISHED DRAFT.

\bibitem{PEG} \texttt{Bryan Ford.} Parsing Expression Grammars: A Recognition-based Syntactic Foundation. In POPL, pages 111–122. ACM, 2004.

\bibitem{CFG} \texttt{Theodore Norvell.} A Short Introduction to Regular Expressions and Context Free Grammars. Software Engineering 7893, Typseset November 8, 2002
	\url{http://www.engr.mun.ca/~theo/Courses/fm/pub/context-free.pdf}

\bibitem{}DeLine, R., Bragdon, A., Rowan, K., Jacobsen, J., Reiss, S.P.: Debugger canvas: industrial experience with the code bubbles paradigm. In: ICSE. (2012) 1064–1073.

\bibitem{java_corpus} The Spring Framework, a comprehensive programming and configuration model for modern Java-based enterprise applications.
\url{https://github.com/spring-projects/spring-framework}

\bibitem{JProfiler} EJTechnology, JProfiler. Java JVM all in one profiler
	\url{http://www.ej-technologies.com/products/jprofiler/overview.html?gclid=EAIaIQobChMImda0lYLD1QIVjxbTCh1qxAXMEAAYASAAEgKca_D_BwE}

\bibitem{economicdebug} The Economic Impacts of Inadequate Infrastructure for Software Testing
\end{thebibliography}